Satellite allignments in galaxy pairs in the Illustris Simulation

### 2016-05-04 paper/ms.tex
new plot

\begin{figure}
\centering
\includegraphics[width=\hsize]{n_structure.pdf}\\
\caption{Number of bright substructures ($M_{B}<-9$) as a function of
  the number of dark substructures around the pair's sphere of influence.}
\label{fig:nstructure}
\end{figure}

@@

\section{Results}
\label{Results}
\begin{figure}
\centering
\includegraphics[width=\hsize]{AxisRatio_RandomMean_VS_Luminous.pdf}\\
\caption{.}
\label{fig:StreamPlaneOrbit}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\hsize]{n_structure.pdf}\\
\caption{Number of bright substructures ($M_{B}<-9$) and dark matter
  substructures.}
\label{fig:nstructure}
\end{figure}

@@

\section{Results}
\label{Results}
\begin{figure}
\centering
\includegraphics[width=\hsize]{axratio_dark_bright.pdf}\\
\caption{Axis ratio of luminous satellites versus the axis ratio for
  dark subhalos.}
\label{fig:StreamPlaneOrbit}
\end{figure}
